IRT procedures for shortening tests

### 2024-10-09 the-good-the-bad-the-ugly.qmd
i give up

---
title: "IRT procedures for shortening tests"
author: "Ottavia M. Epifania & Friends"
format: 
  revealjs: 
    theme: mytheme.scss
background-opacity: "0.45"
title-slide-attributes: 
   data-background-image: "https://psicostat.github.io/shine-bright/gbu.jpg"
   data-background-size: 350px, cover
   data-background-position: 50% 5%, center
server: shiny
---

```{r, setup, include=FALSE}
library(knitr)
library(shiny)
IRT <- function(theta, a = 1, b = 0, c = 0,e = 1) {
  y <- c + (e - c) * exp(a * (theta - b)) / (1 + exp(a * (theta - b)))
  y[is.na(y)] = 1
  return(y)
}

@@

$$P(x_{pi} = 1|\theta_p, b_i, a_i) = \frac{\exp[a_i(\theta_p - b_i)])}{1 + \exp[a_i(\theta_p - b_i)])}$$

@@

@@

>>>>

---
title: "IRT procedures for shortening tests"
author: "Ottavia M. Epifania & Friends"
format: 
  revealjs: 
    theme: mytheme.scss
    logo: "www/psicostat.jpg"
background-opacity: "0.45"
title-slide-attributes: 
   data-background-image: "https://psicostat.github.io/shine-bright/gbu.jpg"
   data-background-size: 350px, cover
   data-background-position: 50% 5%, center
server: shiny
---

```{r, setup, include=FALSE}
library(knitr)
library(shiny)
library(ggplot2)
library(tidyverse)
IRT <- function(theta, a = 1, b = 0, c = 0,e = 1) {
  y <- c + (e - c) * exp(a * (theta - b)) / (1 + exp(a * (theta - b)))
  y[is.na(y)] = 1
  return(y)
}

@@

Item Response Function:

$$P(x_{pi} = 1|\theta_p, b_i, a_i) = \frac{\exp[a_i(\theta_p - b_i)])}{1 + \exp[a_i(\theta_p - b_i)])}$$
<br>

Item Information Function:

@@

<br>

Test Information Function:

@@

## Results

```{r}
load("gbu-comparison.RData")
item_comparison$iter = 1:100
ic_long = pivot_longer(item_comparison, cols = !iter)

ic = ic_long %>%  
  group_by(name) %>%  
  summarise(min = min(value), max = max(value), mean = mean(value), median = mean(value), 
            sd = sd(value))
ggplot(ic, 
       aes(x = name, y = mean, color = name)) + geom_point(shape = 5, size = 3) + ylim(0,6) + 
  geom_errorbar(aes(ymin = mean-sd, ymax = mean+sd), width = .2)+ 
  geom_point(aes(x = name, y = min), shape = 1) + geom_point(aes(x = name, y = max), shape = 15) + 
  geom_point(aes(x = name, y = median), shape = 4, size = 3) + 
  scale_color_manual(values = c("royalblue","red",  "seagreen")) + 
  ylab("Item") + theme_light() + 
  theme(axis.text = element_text(size = 25), 
        axis.title.x = element_blank(), 
        legend.position = "none")

## When $||Q_{ILA}|| = ||Q_{Frank}||$

```{r}
library(patchwork)
equal_IF = as.numeric(rownames(item_comparison[item_comparison$nfrank == item_comparison$nila, ]))
wrap_plots(g[equal_IF])
```
